---
title: "R Notebook"
---

```{r, message=FALSE}
library(openprescribingR)
library(tidyverse)
library(sf)
library(ggiraph)
library(stringr)
```

```{r}
ccggeom <- CCG_boundaries_or_location(as_sf = TRUE) %>%
  slice(-167) %>%
mutate(
    lon = map_dbl(geometry, ~st_centroid(.x)[[1]]),
    lat = map_dbl(geometry, ~st_centroid(.x)[[2]])
    ) 
```

```{r}
ggplot(ccggeom) +
  geom_sf() +
  geom_text(aes(x=lon, y=lat, label=name), hjust = 0, nudge_x = 0.05) + 
  coord_sf(crs= 4326, datum = sf::st_crs(4326))
```

```{r}
gg_point =  ggplot(ccggeom) +
  geom_sf() +
  geom_point_interactive(aes(x = lon, y = lat, tooltip = name)) +
  coord_sf(crs= 4326, datum = sf::st_crs(4326))
ggiraph(code = {print(gg_point)}, width_svg = 17.07, height_svg = 13.46)
```

```{r}
gg_point =  filter(dataframe, date == "2017-05-01") %>%
  ggplot() +
  geom_sf(aes(fill = costperperson)) +
  geom_point_interactive(aes(x = lon, y = lat, tooltip = label)) +
  theme(legend.position="none")
ggiraph(code = {print(gg_point)}, width_svg = 17.07, height_svg = 13.46)
```

rest on post 6. 
```{r, message=FALSE}
spendingdata <- spending_by_practice(BNF_section_code = "2.12", practice_code = "G82732")
spendingdata$date <- as.Date(spendingdata$date)

ccgpracticespendingdata <- spending_by_practice(BNF_section_code = "2.12", CCG_code = "99J")
ccgpracticespendingdata$date <- as.Date(ccgpracticespendingdata$date)

CCGdata <- location_function(CCG_code = "99J", as_sf = TRUE) %>%
mutate(
    lon = map_dbl(geometry, ~st_centroid(.x)[[1]]),
    lat = map_dbl(geometry, ~st_centroid(.x)[[2]])
    )
CCGdata$name <- str_replace_all(CCGdata$name, "'", " ")
ccgpracticespendingdata2 <- spending_by_practice(BNF_section_code = "2.12", CCG_code = "99J") %>%
  group_by(date) %>% 
  summarise(`Q1`=quantile(actual_cost, probs=0.25),
            `Q2`=quantile(actual_cost, probs=0.5),
            `Q3`=quantile(actual_cost, probs=0.75),
            `Min`=min(actual_cost),
            `Max`=max(actual_cost),
            `Total`=sum(actual_cost)) %>%
  mutate(Clinic = spendingdata[, 'actual_cost'])
ccgpracticespendingdata2$date <- as.Date(ccgpracticespendingdata2$date)

tidyr <- ccgpracticespendingdata2 %>%
  gather(key = group, value = actual_cost, -date, -Total) %>%
  select(-Total) %>%
  mutate(label = str_c(date, ": ", group, ", £", actual_cost))
tidyr$date <- as.Date(tidyr$date)
```

```{r}
gg_point = ggplot(CCGdata) +
  geom_sf(data = CCGdata[1,]) +
  geom_point_interactive(data = CCGdata[2:86,], aes(x = lon, y = lat, tooltip = name)) +
  geom_point_interactive(data = CCGdata[57,], aes(x = lon, y = lat, tooltip = name), colour = "red") +
  geom_text(data = CCGdata[57,], aes(x=lon, y=lat, label=name), hjust = 0, nudge_x = 0.05) + 
  theme(legend.position="none") +
  coord_sf(crs= 4326, datum = sf::st_crs(4326))

ggiraph(code = {print(gg_point)}, width_svg = 17.07, height_svg = 14.75)

gg_point = ggplot(spendingdata) +
  geom_ribbon(data = ccgpracticespendingdata2, 
              aes(x = date, ymin = Min, ymax = Max), alpha=0.75, fill = "grey80") +
  geom_ribbon(data = ccgpracticespendingdata2, 
              aes(x = date, ymin = Q1, ymax = Q3), alpha=0.75, fill = "grey70") +
  geom_line_interactive(data = filter(tidyr, group=="Q3"|group=="Q1"),
            aes(x= date, y=actual_cost, group=group, colour=group, tooltip = label), colour = "grey70") +
  geom_line_interactive(data = filter(tidyr, group=="Max"|group=="Min"),
            aes(x= date, y=actual_cost, group=group, colour=group, tooltip = label), colour = "grey80") +
  geom_line_interactive(data = filter(tidyr, group=="Clinic"|group=="Q2"),
            aes(x= date, y=actual_cost, group=group, colour=group, tooltip = label), alpha=0.5, size=2) + 
  theme(axis.text.x=element_text(angle=45, hjust = 1)) +
  labs(title="Actual_cost on 'BNF Section 2.12 Drugs - Lipid-Regulating Drugs'")

ggiraph(code = {print(gg_point)}, width_svg = 17.07, height_svg = 7.375)
```

gg_point = ccgpracticespendingdata %>%
  ggplot() +
  geom_step_interactive(aes(x= date, y=actual_cost, group=row_id, tooltip = label)) +
  geom_step_interactive(data = filter(tidyr, group=="Clinic"|group=="Q2"),
            aes(x= date, y=actual_cost, group=group, colour=group, tooltip = label), 
            size=2) + 
  geom_text(data = filter(ccgpracticespendingdata, date == "2017-05-01"), aes(label = row_id, x=date, y=actual_cost, 
    vjust = 1, hjust = 0, angle=45)) +
  theme(axis.text.x=element_text(angle=45, hjust = 1)) +
  labs(title="Actual_cost spending on 'BNF Section 2.12 Drugs - Lipid-Regulating Drugs'")

ggiraph(code = {print(gg_point)})

N.B no geom_step_interactive function.

```{r}
ccgpracticespendingdata$date <- as.Date(ccgpracticespendingdata$date)
ccgpracticespendingdata <- ccgpracticespendingdata %>%
  mutate(label = str_c(date, ": ", row_name, ", ", actual_cost))

ccgpracticespendingdata2 <- ccgpracticespendingdata2 %>%
  mutate(label = str_c(date, ": ", row_name, ", ", actual_cost))

ccgpracticespendingdata$label <- str_replace_all(ccgpracticespendingdata$label, "'", " ")
tidyr$label <- str_replace_all(tidyr$label, "'", " ")

```


```{r}
gg_point = ccgpracticespendingdata %>%
  ggplot() +
   geom_ribbon(data = ccgpracticespendingdata2, 
              aes(x = date, ymin = Min, ymax = Max), fill = "grey80", alpha=0.75) +
  geom_ribbon(data = ccgpracticespendingdata2, 
              aes(x = date, ymin = Q1, ymax = Q3), fill = "grey70", alpha=0.75) +
  
  
  geom_line_interactive(aes(group = row_id, x=date, y=actual_cost, tooltip = label)) +
  
  geom_line_interactive(data = filter(tidyr, group=="Clinic"|group=="Q2"),
            aes(x= date, y=actual_cost, group=group, colour=group, tooltip = label), 
            size=2) + 
  
  
  geom_text(data = filter(ccgpracticespendingdata, date == "2017-05-01"), aes(label = row_id, x=date, y=actual_cost, 
    vjust = 1, hjust = 0, angle=45)) +
  theme(axis.text.x=element_text(angle=45, hjust = 1)) +
  labs(title="Actual_cost spending on 'BNF Section 2.12 Drugs - Lipid-Regulating Drugs'")

ggiraph(code = {print(gg_point)}, width_svg = 17.07, height_svg = 7.375)
```

ggiraph(code = {print(gg_point)}, width_svg = 17.07, height_svg = 8.12)
http://auctionrepair.com/pixels.html

